Rebuttal JMLR 14-133

### 2014-09-05 pkg/partykit/inst/mloss/review2/p2p.tex
note demo
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@599 255f4249-2263-4417-b1ea-8498779e27a7

We also added an example showing how the partykit infrastructure can be used
to quickly implement model assessment strategies.

@@

see additions to constparty vignette
<Z FIXME>

@@

demo mit mlbench:Satellite und rpart und J4.8

>>>>

We added an example showing how the partykit infrastructure can be used
to quickly implement model assessment strategies to the end of Section~3 in
the constparty vignette.

@@

Please see the new example in Section~3 of the constparty vignette.
<Z FIXME>

@@

We added a demo (executable via demo("memory-speed")) that compares object
sizes and prediction speed for larger rpart and J48 trees.
